---
title: "Reproducibility Report: Group B Choice 3"
output:
  html_document:
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

-------

For this exercise, please try to reproduce the results from Experiment 2 of the associated paper (de la Fuente, Santiago, Roman, Dumitrache, & Casasanto, 2014). The PDF of the paper is included in the same folder as this Rmd file. 

#### Methods summary: 

Researchers tested the question of whether temporal focus differs between Moroccan and Spanish cultures, hypothesizing that Moroccans are more past-focused, whereas Spaniards are more future-focused. Two groups of participants ($N = 40$ Moroccan and $N=40$ Spanish) completed a temporal-focus questionnaire that contained questions about past-focused ("PAST") and future-focused ("FUTURE") topics. In response to each question, participants provided a rating on a 5-point Likert scale on which lower scores indicated less agreement and higher scores indicated greater agreement. The authors then performed a mixed-design ANOVA with agreement score as the dependent variable, group (Moroccan or Spanish, between-subjects) as the fixed-effects factor, and temporal focus (past or future, within-subjects) as the random effects factor. In addition, the authors performed unpaired two-sample t-tests to determine whether there was a significant difference between the two groups in agreement scores for PAST questions, and whether there was a significant difference in scores for FUTURE questions.

------

#### Target outcomes: 

Below is the specific result you will attempt to reproduce (quoted directly from the results section of Experiment 2):

> According to a mixed analysis of variance (ANOVA) with group (Spanish vs. Moroccan) as a between-subjects factor and temporal focus (past vs. future) as a within-subjectS factor, temporal focus differed significantly between Spaniards and Moroccans, as indicated by a significant interaction of temporal focus and group, F(1, 78) = 19.12, p = .001, ηp2 = .20 (Fig. 2). Moroccans showed greater agreement with past-focused statements than Spaniards did, t(78) = 4.04, p = .001, and Spaniards showed greater agreement with future-focused statements than Moroccans did, t(78) = −3.32, p = .001. (de la Fuente et al., 2014, p. 1685).

------

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

# Step 1: Load packages

```{r}
library(tidyverse) # for data munging
library(knitr) # for kable table formating
library(haven) # import and export 'SPSS', 'Stata' and 'SAS' Files
library(readxl) # import excel files
library(rstatix)

# #optional packages/functions:
# library(afex) # anova functions
# library(ez) # anova functions 2
# library(scales) # for plotting
# std.err <- function(x) sd(x)/sqrt(length(x)) # standard error
```

# Step 2: Load data

```{r}
# Just Experiment 2
data_path <- 'data/DeLaFuenteEtAl_2014_RawData.xls'
d <- read_excel(data_path, sheet=3)
```

# Step 3: Tidy data

```{r}
d = rename(d, Agreement = "Agreement (0=complete disagreement; 5=complete agreement)")
```


```{r}
is_empty(d)
```


```{r}
colnames(d)
```

# Step 4: Run analysis

## Pre-processing

```{r}
tidy_d =d %>% 
  group_by(participant, group, subscale) %>% 
  summarise(Mean_participant_rating = mean(Agreement)) 
tidy_d
```


```{r}
nrow(tidy_d)
```


```{r}
summary_d = d %>%
  group_by(group, subscale)  %>%
summarize(Rating = mean(Agreement), sem = sd(Agreement)/sqrt(length(Agreement))) 

summary_d
```

```{r}
level_order <- factor(summary_d$group, level = c('young Spaniard', 'Moroccan'))
scale_order <- factor(summary_d$subscale, level = c('PAST', 'FUTURE'))
```

## Descriptive statistics

Try to recreate Figure 2 (fig2.png, also included in the same folder as this Rmd file):

```{r}
p<-ggplot(data=summary_d, aes(x=level_order, y=Rating, fill = scale_order)) +
  geom_bar(position="dodge", stat="identity",colour="black", # Use black outlines,
             size=.1) + 
  geom_errorbar(aes(ymin=Rating-sem, ymax=Rating+sem),width=.1,position=position_dodge(.9)) + 
  ylim(0, 4.0)
p

```

## Inferential statistics

> According to a mixed analysis of variance (ANOVA) with group (Spanish vs. Moroccan) as a between-subjects factor and temporal focus (past vs. future) as a within-subjects factor, temporal focus differed significantly between Spaniards and Moroccans, as indicated by a significant interaction of temporal focus and group, F(1, 78) = 19.12, p = .001, ηp2 = .20 (Fig. 2).

```{r}
# reproduce the above results here
d %>% anova_test(Agreement ~ group *  subscale)

```

> Moroccans showed greater agreement with past-focused statements than Spaniards did, t(78) = 4.04, p = .001, 

```{r}
# reproduce the above results here
t.test(Mean_participant_rating ~ group, data = filter(tidy_d, subscale == "PAST") )
```

> and Spaniards showed greater agreement with future-focused statements than Moroccans did, t(78) = −3.32, p = .001.(de la Fuente et al., 2014, p. 1685)

```{r}
# reproduce the above results here
t.test(Mean_participant_rating ~ group, data = filter(tidy_d, subscale == "FUTURE") )
```

# Step 5: Reflection

Were you able to reproduce the results you attempted to reproduce? If not, what part(s) were you unable to reproduce?

> I was able to reproduce the descriptive stats, but not the inferential stats. 

How difficult was it to reproduce your results? 

> Medium difficult. 

What aspects made it difficult? What aspects made it easy?

> I think the ANOVA part was difficult because I was not sure which specific setting I should use. And I was also unsure which t-test I should use. 
