---
title: "Reproducibility Report: Group A Choice 1"
output:
  html_document:
    toc: true
    toc_float: true
---

-------

For this exercise, please try to reproduce the results from Study 1 of the associated paper (Joel, Teper, & MacDonald, 2014). The PDF of the paper is included in the same folder as this Rmd file. 

#### Methods summary: 

In study 1, 150 introductory psychology students were randomly assigned to a "real" or a "hypothetical" condition. In the real condition, participants believed that they would have a real opportuniy to connect with potential romantic partners. In the hypothetical condition, participants simply imagined that they are on a date. All participants were required to select their favorite profile and answer whether they were willing to exchange contact information. 

------

#### Target outcomes: 

Below is the specific result you will attempt to reproduce (quoted directly from the results section of Study 1):

>> We next tested our primary hypothesis that participants would be more reluctant to reject the unattractive date when they believed the situation to be real rather than hypothetical. Only 10 of the 61 participants in the hypothetical condition chose to exchange contact information with the unattractive potential date (16%). In contrast, 26 of the 71 participants in the real condition chose to exchange contact information (37%). A chi-square test of independence indicated that participants were significantly less likely to reject the unattractive potential date in the real condition compared with the hypothetical condition, X^2(1, N = 132) = 6.77, p = .009.

------

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

# Step 1: Load packages

```{r}
library(tidyverse) # for data munging
library(knitr) # for kable table formating
library(haven) # import and export 'SPSS', 'Stata' and 'SAS' Files
library(readxl) # import excel files
library(dplyr)
library(janitor)

# #optional packages:
# library(broom)
# library(labelled)# converts SPSS's labelled to R's factor 
```

# Step 2: Load data

```{r}
# Just Study 1
d <- read_sav('data/Empathy Gap Study 1 data.sav')
```

# Step 3: Tidy data

```{r}
new_d <- d[, c('ID', 'condition', 'exchangeinfo')]
new_d
```


```{r}
# hypothetical condition (0)
new_condition_0 <- new_d %>% 
  filter(condition== 0)
```


```{r}
new_condition_1 <- new_d %>% 
  filter(condition== 1)
```

# Step 4: Run analysis

## Descriptive statistics

> Only 10 of the 61 participants in the hypothetical condition chose to exchange contact information with the unattractive potential date (16%). In contrast, 26 of the 71 participants in the real condition chose to exchange contact information (37%).

```{r}
# reproduce the above results here
# In the hypothetical condition, 10 out of 61 participants chose to exchange info. 
new_condition_0
new_condition_0 %>% count(exchangeinfo)
```


```{r}
# In the real condition, 21 out of 71 participants chose to exchange info. 
new_condition_1 %>% count(exchangeinfo)
```

## Inferential statistics

> A chi-square test of independence indicated that participants were significantly less likely to reject the unattractive potential date in the real condition compared with the hypothetical condition, X^2(1, N = 132) = 6.77, p = .009.

Hint: if you are using the function chisq.test(), make sure to set the continuity correction to false ("correct = FALSE") since sample size is greater than 20. 

```{r}
# reproduce the above results here
new_d_for_test <-d  %>%
  tabyl(exchangeinfo, condition)
new_d_for_test
```


```{r}
chisq.test(new_d_for_test)
```

# Step 5: Reflection

Were you able to reproduce the results you attempted to reproduce? If not, what part(s) were you unable to reproduce?

> I could not reproduce the Chi-squared test (but maybe I used the test wrong). 

How difficult was it to reproduce your results? 

> I think this study was not difficulty. 

What aspects made it difficult? What aspects made it easy?

> I was confused by the data coding. For example, I could not figure out whether condition = 0 was hypothetical or real condition untill I finished counting. 


